### 2014-11-11 motivation.tex
edits

\begin{codehaskell}
type Operation = forall e a r. [e] -> a -> (r, Maybe e)
\end{codehaskell}

@@

getBalance :: [Acc] -> () -> (Int, Maybe Acc)
getBalance ctxt _ =
  let res = sum [x | Deposit x <- ctxt]
						- sum [x | Withdraw x <- ctxt]
	in (res, Nothing)

deposit :: [Acc] -> Int -> ((), Maybe Acc)
deposit _ amt = (amt, Just dollar Deposit amt)

withdraw :: [Acc] -> Int -> (Bool, Maybe Acc)
withdraw ctxt v =
	if sel1 dollar getBalance ctxt () >= v
  then (True, Just dollar Withdraw v)
	else (False, Nothing)
\end{codehaskell}
\caption{Definition of a bank account expressed in Quelea.}
\label{fig:ex}
\end{figure}

>>>>

\begin{codehaskell}
type Operation e a r = [e] -> a -> (r, Maybe e)
\end{codehaskell}

@@

getBalance :: Operation Acc () Int
getBalance ctxt _ =
  let res = sum [x | Deposit x <- ctxt]
						- sum [x | Withdraw x <- ctxt]
	in (res, Nothing)

deposit :: Operation Acc Int ()
deposit _ amt = (amt, Just dollar Deposit amt)

withdraw :: Operation Acc Int Bool
withdraw ctxt v =
	if sel1 dollar getBalance ctxt () >= v
  then (True, Just dollar Withdraw v)
	else (False, Nothing)
\end{codehaskell}
\caption{Definition of a bank account expressed in Quelea.}
\label{fig:ex}
\end{figure}
